QPLIB: A Library of Quadratic Programming Instances

### 2018-02-12 QPLIB-3.tex
Update QPLIB-3.tex

In addition to these spontaneous contributions we analyzed existing generic
libraries of instances available  on the internet that contain QP
instances. Namely, the libraries from which we gathered instances are
%
\begin{itemize}
 \item the \texttt{BARON} library
 \url{http://www.minlp.com/nlp-and-minlp-test-problems};
%
\item the \texttt{CUTEst} library
 \url{https://ccpforge.cse.rl.ac.uk/gf/project/cutest};
%
\item the \texttt{GAMS Performance} libraries
 \url{http://www.gamsworld.org/performance/performlib.htm};
%
\item the \texttt{MacMINLP} library
 \url{https://wiki.mcs.anl.gov/leyffer/index.php/MacMINLP};
%
\item the \texttt{Maros-M{\'e}sz{\'a}ros} library
 \url{http://www.doc.ic.ac.uk/~im/00README.QP};
%
\item the \texttt{MINLP} library
 \url{http://www.gamsworld.org/minlp/minlplib.htm};
%
\item the \texttt{POLIP} library
 \url{http://polip.zib.de/pipformat.php}.
\end{itemize}

Other quadratic instances were found in online libraries devoted to
specific QP problems as Max-Cut, Quadratic Assignment, Portfolio
Optimization, and several others. \textcolor{red}{In addition, we mention
that other generic libraries exist, e.g., 
Conic library CBLIB (\url{http://cblib.zib.de}) and 
MIPLIB~2010 (\url{http://miplib.zib.de/}), to mention just a few.}\todo{AG: maybe cite CBLIB paper \cite{Friberg2016}}

@@

The QPLIB instances are publicly accessible at the website \url{http://qplib.zib.de}, which was created by extending
scripts and tools initially developed for MINLPLib\,2~\cite{Vigerske2014}.
%
We provide all instances in GAMS (\texttt{.gms}), AMPL (\texttt{.mod}), CPLEX (\texttt{.lp})
\cite{,cplex}, and  QPLIB (\texttt{.qplib}) formats. The latter is a new format
specifically for QP instances. In comparison to more \emph{high level}
formats such as \texttt{.gms} and \texttt{.lp}, the new
format offers three main advantages: it is easier to read by a stand-alone
parser (provided)\todo{SV: what is meant by ``(provided)''?}, it typically produces smaller files, and it permits the
inclusion of two-sided inequalities without needless repetition of data.
%the order of variables and constraints is fixed.
See Appendix~\ref{sec:format} for more details.

>>>>

In addition to these spontaneous contributions we analyzed existing generic
libraries of instances available  on the internet that contain QP
instances. Namely, the libraries from which we gathered instances are
%
\begin{itemize}
 \item the \texttt{BARON} library
 \url{http://www.minlp.com/nlp-and-minlp-test-problems};
%
\item the \texttt{CUTEst} library
 \url{https://ccpforge.cse.rl.ac.uk/gf/project/cutest};
%
\item the \texttt{GAMS Performance} libraries
 \url{http://www.gamsworld.org/performance/performlib.htm};
%
\item the \texttt{MacMINLP} library
 \url{https://wiki.mcs.anl.gov/leyffer/index.php/MacMINLP};
%
\item the \texttt{Maros-M{\'e}sz{\'a}ros} library
 \url{http://www.doc.ic.ac.uk/~im/00README.QP};
%
\item the \texttt{MINLPLib} library
 \url{http://www.gamsworld.org/minlp/minlplib.htm};
%
\item the \texttt{POLIP} library
 \url{http://polip.zib.de/pipformat.php}.
\end{itemize}

Other quadratic instances were found in online libraries devoted to
specific QP problems as Max-Cut, Quadratic Assignment, Portfolio
Optimization, and several others. \textcolor{red}{In addition, we mention
that other generic libraries exist, e.g., 
Conic library CBLIB (\url{http://cblib.zib.de}) and 
MIPLIB~2010 (\url{http://miplib.zib.de/}), to mention just a few.}
%\todo{AG: maybe cite CBLIB paper \cite{Friberg2016} SV: then we would have to add citations for all mentioned libraries (where available)}

@@

The QPLIB instances are publicly accessible at the website \url{http://qplib.zib.de}, which was created by extending
scripts and tools initially developed for MINLPLib\,2~\cite{Vigerske2014}.
%
We provide all instances in GAMS (\texttt{.gms}), AMPL (\texttt{.mod}), CPLEX (\texttt{.lp})
\cite{,cplex}, and  QPLIB (\texttt{.qplib}) formats. The latter is a new format
specifically for QP instances. In comparison to more \emph{high level}
formats such as \texttt{.gms} and \texttt{.lp}, the new
format offers three main advantages: it is easier to read by a stand-alone
parser, 
%(provided)\todo{SV: what is meant by ``(provided)''?}, 
it typically produces smaller files, and it permits the
inclusion of two-sided inequalities without needless repetition of data.
%the order of variables and constraints is fixed.
See Appendix~\ref{sec:format} for more details.
